\documentclass[a4paper,11pt]{article}
\usepackage[utf8]{inputenc}
\begin{document}
\noindent
\begin{center}
\Large\textbf{RITS System Architecture}
\end{center}

\vspace{1cm}
\noindent
To use RITS, add the following line to your Prolog code:

\bigskip
\textbf{:- use\_module(rits).}
\bigskip

\noindent RITS is accessible via the following API calls:

\begin{itemize}
\item \textbf{rits\_start(-Start)}\\\textbf{Start} is unified with a
  Prolog term that represents the initial state of RITS, before the
  system has received any user actions.

\item \textbf{rits\_next\_action(+A0, -A, +S0, -S)}\\
  This predicate relates a user action \textbf{A0} and a RITS state
  \textbf{S0} to the next RITS action \textbf{A} and next
  state~\textbf{S}.

\item \textbf{rits\_history(+S, -Hist)}\\
  \textbf{Hist} is unified with a list of Prolog terms that represent
  the history of user interactions up to and including state~\textbf{S}.
\end{itemize}

These predicates are completely \textit{pure}: They no not emit any
output, do not write any files, and do not query the user in any way.
Therefore, they can be quite safely executed in a hosting environment.

User actions are described in Table~\ref{tab:useractions}. The most
important RITS actions are described in Table~\ref{tab:ritsactions}.
RITS clients are expected to interpret RITS actions ``appropriately'',
such as: displaying messages on the terminal or via HTML, allowing
users to give answers etc.

\begin{table}[ht]
  \centering
  \begin{tabular}{cp{7cm}}
    \hline
    \textbf{solve(Task)} & Guide the student through solving \textbf{Task}.\\
    \textbf{student\_answers(T)} & Tell RITS that the student has responded with \textbf{T}. This action is only admissible if the directly preceding RITS action was \textbf{read\_answer}.\\
    \textbf{next} & Query RITS for its next action. \\
    \textbf{skip} & The student wants to skip solving the subproblem that is
    currently in progress. (\textit{TODO})\\
    \hline
  \end{tabular}
\caption{Admissible user actions}
  \label{tab:useractions}
\end{table}

\begin{table}[ht]
  \centering
  \begin{tabular}{cp{7cm}}
    \hline
    \textbf{enter} & Start of a subproblem that the student must solve.\\
    \textbf{exit} & The most recently spawned subproblem was solved.\\
    \textbf{format(F)} & The string \textbf{F} is to be displayed.\\
    \textbf{format(F,As)} & The format string \textbf{F} is to be displayed. \textbf{As} is a list of arguments that are output, in sequence, in place of each \texttt{\~\ $\!\!\!$w} that appears in \textbf{F}.\\
    \textbf{read\_answer} & The student is to be queried for a an answer.\\
    \textbf{solve(Task)} & The student should be given the task \textbf{Task}.\\
    \textbf{done} & There are no further actions.\\
    \hline
  \end{tabular}
\caption{The most important RITS actions}
  \label{tab:ritsactions}
\end{table}


\vspace{0.7cm}

Due to their purity, these predicates are also very amenable to
regression testing and further analysis. (\textit{more to follow})

\vspace{0.7cm}

The RITS engine may be accessed directly via Prolog, remotely via
JavaScript and \textit{pengines}, or via any other language embedding.

\bigskip
\begin{center}
  \large\textbf{Extending RITS}
\end{center}

\medskip
\noindent Internally, RITS uses the following predicates to decide
what to do. All of them are DCG rules that describe a list of RITS
actions that need to be performed in response to certain user actions.

\begin{itemize}
\item \textbf{rits:solve//1}: this is called with argument \textbf{Task}
  for user actions of the form \textbf{solve(Task)}.

\item \textbf{rits:actions//3}: This is called with arguments \textbf{Task}
  and \textbf{Answer} after the user answered the question posed after
  \textbf{solve(Task)} with \textbf{Answer}. The third argument is a
  Prolog representation of previous interactions of the form
  \textbf{T=A}.

\end{itemize}

RITS can be extended in a \textit{modular} way to handle new domains.
To teach RITS additional rules, define a Prolog module that provides
its own (additional) DCG rules for \textbf{rits:solve//1} and
\textbf{rits:actions//3}. 

In these DCG rules, modules may provide their own custom RITS actions
as Prolog terms that must be handled by the client when they appear as
a RITS action upon calling \textbf{rits\_next\_action/4}.

See the file \textbf{rits\_multiple\_choice.pl} for the definition of
simple multiple choice tests that are repeated when wrong answers are
given.

\bigskip
\begin{center}
  \large\textbf{LORITS: The extensible language of RITS}
\end{center}

\medskip
\noindent
Preparing teaching material and exercises for students is one of the
most common and essential tasks that teachers need to perform
every day. It requires judicious human creativity and knowledge and
cannot be automated.

Describing the material that is to be taught is a \textit{declarative}
activity: We primarily want to describe \textit{what} should be
presented to students. \textit{How} it is presented can vary by
circumstances. For example, on a text terminal, we expect a different
presentation of the material than on mobile phones and on Braille
terminals.

RITS makes it easy for you to declaratively describe \textit{what}
should be done. RITS comes with built-in modules that describe what it
means for students to ``solve'' a task like canceling fractions. In
addition, you can supply your own rules for RITS, thereby stating what
you mean by custom tasks that you define for your students.

The language of RITS is called LORITS and lets you state actions that
need to be performed in order for students to ``solve'' a task. For
example, it is easy to declaratively describe your ``Lesson 1'', which
may consist of showing a video that contains some facts, and then have
students automatically go through a custom multiple-choice test that
asks them questions about the video in order to assess their
understanding:

\begin{verbatim}
 rits:solve(lesson_1) -->
         [video("http://www.youtube.com/VideoAboutMozambique"),
          solve(mchoice("What is the capitol of Mozambique?\n",
                        ['Maputo','Pretoria',
                         'Nairobi','Vienna'], 1)),
          done].
\end{verbatim}

LORITS provides predefined actions such as formatting texts, going
through multiple-choice tests, playing videos etc., which makes it
easy to put together custom lessons that students can work through.

\bigskip \textit{Here, it is our task to provide teachers with
  suitable building blocks of RITS actions, so that custom lessons can
  be put together quickly, possibly with our initial assistance. The
  task here is to find good and versatile actions to cover a large
  variety of interaction styles.}

\vfil
\end{document}

